%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile.png}
\name{Jay}{Morelli}
\position{Software Developer{\enskip\cdotp\enskip}Tech Lead}
\address{Portugal}

\mobile{(+351) 911 763 499}
\email{jcrmorelli@gmail.com}
\dateofbirth{April 16, 1996}
\homepage{www.jaymorelli.me}
\github{jaymorelli96}
\linkedin{jaymorelli}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}


%-------------------------------------------------------------------------------
\begin{document}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient{c/side}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Senior Software Engineer (Go/Rust)}
% How the letter is opened
\letteropening{Dear c/side team,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Jay Morelli~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am a passionate and dedicated Tech Lead and Software Engineer with a B.S. in Computer Engineering from the University of Algarve. Currently, I work at Siemens, where I have played a key role in the Industrial Edge project. My journey in software engineering has been driven by a deep love for technology and a commitment to excellence. I thrive on solving complex problems, sharing knowledge, and contributing to a collaborative team environment.

My strongest trait is my passion, which fuels my work and drives me to continuously improve. I believe that this passion, combined with my strong set of soft skills, has been what have always set me apart. In my role I am always providing technical guidance, engaging in pair programming, and acting as a gatekeeper for quality and standards. My role involves significant cross-team collaboration, including bi-weekly architectural syncs with the software architect, where I am always vocal and eager to discuss and share technical topics.

\lettersection{Why c/side?}
I am particularly drawn to c/side because of its innovative approach to web security where others have not paid attention and because of its mission to democratize web security and make it accessible to all, regardless of the size of the venture. The opportunity to be part of a startup that is at the forefront of protecting critical information and systems is incredibly exciting. I am impressed by the company's vision and the potential impact it can have in the industry.

c/side's commitment to addressing the often-overlooked area of client-side security, using AI to solve long-standing issues, and developing a 3rd party script proxy, performance, and analysis engine aligns perfectly with my passion for innovative solutions. This approach not only addresses critical threats but also provides a comprehensive and elegant solution that allows security teams to feel confident and secure. I am inspired by c/side's vision and eager to contribute my technical expertise to help realize this important mission.

\lettersection{Why Me?}
I believe I am an ideal fit for the Software Engineer position at c/side because of my unique blend of technical expertise, collaborative spirit, and passion for innovation. At Siemens, I am leading the development of the Twin feature, inspired by the Kubernetes Operator Pattern. My proactive approach in mentoring and supporting my team members, along with my contributions to architectural decisions and onboarding processes, has been pivotal to our project's success.

My ability to communicate effectively, inspire others, and foster a supportive team environment makes me well-suited for this role. I am confident that my background, skills, and passion align well with the goals of c/side, and I am eager to bring my expertise to your team.

Thank you for considering my application. I look forward to the opportunity to discuss how my experiences and motivations can contribute to the success of your team. Please feel free to contact me at +351 911 763 499 or via email at jcrmorelli@gmail.com to schedule an interview.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
